Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-07 Paper/paper.tex
Additional edits from the draft

\subsection{Selenium}
Selenium\cite{Selenium} is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the enjoyment of watching the tests execute.

Nonetheless, we still looked at two options that we will outline briefly below for other developer's reference.

\subsubsection{PhantomJS}
The reigning king of headless browsers is PhantomJS\cite{PhantomJS}. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

\subsubsection{ZombieJS}
ZombieJS\cite{ZombieJS} is often the other go-to for headless browsers. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

\subsection{Jenkins}
Jenkins\cite{Jenkins} is the first of the continuous integration frameworks that we tried out. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members. \cite{JenkinsGitHub} Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{Figure}[!ht]
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}

@@

One of the exceptional strengths of Jenkins is that the developer is only limited by the hardware of the machine running Jenkins. Any increase in computing power will be directly usable by Jenkins. Jenkins can run as many jobs as the server can handle at one time.

@@

Jenkins is an exceptionally strong tool for CI, but requires immense overhead in setting up the environment to run a project in. However, once the server has the necessary applications and libraries, the builds and tests will run without issue. Jenkins can run an ``unlimited'' number of builds, tests, and processes with the only limiting factor the hardware that it is running on. It is also 100\% free and can connect with public and private repositories alike.

\subsection{Travis}
Travis\cite{Travis} is an online continuous integration framework with 29 members and 64 repositories at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the developer more processing power and access to private repositories.

@@

\subsection{Semaphore}
Semaphore\cite{Semaphore} is another online CI framework that connects to GitHub to bring in projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with public and private repositories but requires a subscription after 30 days no matter which repositories are used.

@@

\subsection{MagnumCI}
MagnumCI\cite{MagnumCI} is another online CI framework, it appears that Jenkins is one of the only ``off-line'' CI systems. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects, and that's what we care about.

@@

Drone.io offers support for most of the databases we've heard of, has a variety of deployment options, and is entirely configurable from the online dashboard. It also offers the most browsers and headless browsers for use with web page testing tools such as Selenium and PhantomJS.

@@

Of particular interest is that last feature, \lstinline{watch}. We are particularly fond of grunt's \lstinline{watch} capability because it means that we have tests running near constantly that give immediate feedback to the developer when they change existing code or write new code after having written a test for it. As long as all the tests are passing, the developer has a good idea that the changes made are regression-tested as well as freshly tested and are ready for publishing or integration.

@@

\normalsize
%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
In this chapter, we will outline our final choices for frameworks and why we chose them.

\section{Chosen Toolset}
After evaluating a number of different combinations and tools, we came to the following setup:
\begin{itemize}
  \item Unit Testing: Mocha with Chai.js
  \item Continuous Integration: MagnumCI
  \item Browser Testing: Nightwatch
  \item Misc:
    \begin{itemize}
      \item Coverage: Istanbul
      \item Task Runner: Grunt
      \item Package Manager: NPM (sort of a given when working with Node.js)
    \end{itemize}
\end{itemize}

@@

Mocha was chosen over QUnit because of the ability to structurally portray test suites. Although we loved QUnit's output, the ability to scan code more efficiently won out in the end.

@@

\subsection{MagnumCI}
With all of the features that MagnumCI currently offers for free, we couldn't pass it up. We are still confident that the features needed by an open-source developer will continue to be free after MagnumCI ends its open-beta period.

Quite frankly, we did not have the time nor interest in setting up our own Jenkins server. Given enough resources and time, Jenkins will surely beat all of the rest of the CI frameworks. However, there's something to be said for ease of setup and total time to first use of a tool.

MagnumCI was chosen over Travis because our evaluation application was not on GitHub. Travis is still an incredible CI framework that has some of the best documentation we've seen.

Semaphore was out of the running due to its lack of support for JavaScript and Node.js projects as well as the GitHub requirement.

@@

Overall, the CI frameworks were all impressive and usable. The main driving factor was simply that we didn't have our application on any of the more common repositories and at the time of this writing our application was closed-source. We have every intention of opening it to the public as soon as we get a version that is more polished.

@@

Nightwatch was chosen over Intern's UI testing tool because of the issue with Intern running its own server. If Intern did not impose its own server for what it calls ``functional'' testing, we would probably have gone with Intern for both Unit and UI testing but it did not make sense for us to split up Intern's functionality since we couldn't use it all.

@@

Istanbul was chosen because we had seen it in use with Intern and after minimal research found that it was easy to set up and get running.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Product 
%%% User Manual
%%%   Tools (programs, IDEs, scripts)
%%%   Setup instructions
%%%   Usage
%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Product}
In this section we will mention our development setup, discuss how to set up the chosen tools, and outline our recommended workflow using the tools. It is our hope that after finishing this section, the reader will be able to install and run the chosen tools and have a good grasp of what the next steps are for their particular project.

\section{Our Setup}
The following are the specs of the laptop that we used for the entirely of this research and implementation:
\begin{itemize}
  \item Model: 15-inch Macbook Pro, Late 2008
  \item OS: OS X 10.9.2, Mavericks
  \item Processor: 2.53 GHz Intel Core 2 Duo
  \item Memory: 4 GB 1067 MHz DDR3
  \item Graphics: NVIDIA GeForce 9400M 256 MB
\end{itemize}
The point of listing the laptop specs is to show that our research and workflow was completed on an average, everyday laptop and does not require any kind of special hardware or software configurations.

@@

\section{Tool Setup}
Getting the tools up and running is a fairly simple task. It involves installing modules with NPM, writing or copying a few configuration scripts, and then knowing the right commands.

We decided to install the node modules globally because it made writing our scripts easier, but it's not a requirement. Tests can be executed using locally installed node modules. Instead of using the command by itself, the developer would just need to supply the full path to the executable, which is generally \lstinline{PATH_TO_REPO/node_modules/MODULE_NAME/bin/MODULE_NAME} \space .

>>>>

\subsection{Selenium}
Selenium\cite{Selenium} is an automated browser driver. It is one of the only automated browser drivers; in all of our searching, we did not find a single other browser automation tool, all other frameworks were built on top of Selenium. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

@@

\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the added complexity of running headless browsers.

Nonetheless, we still looked at two options that we will outline briefly below for other developers' reference. The two options outlined below by no means cover all of the headless browser options, they are simply the two that we saw most often discussed by the other testing tools.

\subsubsection{PhantomJS}
PhantomJS\cite{PhantomJS} came up repeatedly in our searches for testing frameworks as an option for headless browsing; it is the reason we had the idea to look into headless browsers. PhantomJS is a headless browser written using WebKit, which is what most of the web is based on. This means that running PhantomJS is nearly indistinguishable from a normal browser to any testing code.

@@

\subsubsection{ZombieJS}
ZombieJS\cite{ZombieJS} is the other headless browser that we saw when searching for browser testing tools. ZombieJS is not a WebKit implementation but rather a simple DOM emulator. This means that certain tests may not be as accurate as they could be with PhantomJS.

@@

\subsection{Jenkins}
Jenkins\cite{Jenkins} is an offline Continuous Integration tool, the only offline tool that we found with active developement and support. It was created by developers of a previous tool called Hudson when a dispute with Oracle led them to fork the Hudson project and rename it Jenkins. As of February 2014, the Jenkins organization has over 1,100 public repositories and 570 members. \cite{JenkinsGitHub} Jenkins has, according to their website, two main focuses: (1) building and testing software continuously and (2) monitoring executions of externally-run jobs. The first focus is the general goal for any CI framework. The second focus is of note and will be discussed after the initial evaluation.

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}

@@

One of the exceptional strengths of Jenkins is that the developer is only limited by the hardware of the machine running Jenkins. Jenkins can run an ``unlimited'' number of builds, tests, and processes with the only limiting factor the hardware that it is running on.

@@

Jenkins is an exceptionally strong tool for CI, but requires immense overhead in setting up the environment to run a project in. However, once the server has the necessary applications and libraries, the developer can run builds and tests. Jenkins is 100\% free and can connect with public and private repositories alike.

\subsection{Travis}
Travis\cite{Travis} is an online continuous integration framework with 29 active developers working to improve it and 64 repositories that support it at the time of this writing. Unlike Jenkins, Travis is all online and includes a dashboard from which the developer can monitor builds and processes. Travis has a free version which is fully-featured but requires the project to be open-source and a paid version which gives the developer more processing power and access to private repositories.

@@

\subsection{Semaphore}
Semaphore\cite{Semaphore} is an online CI framework that connects to GitHub to bring in projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with public and private repositories but requires a subscription after 30 days no matter which repositories are used.

@@

\subsection{MagnumCI}
MagnumCI\cite{MagnumCI} is another online CI framework. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects.

@@

Drone.io offers support for an impressive number of databases, has a variety of deployment options, and is entirely configurable from the online dashboard. It also offers the most browsers and headless browsers for use with web page testing tools such as Selenium and PhantomJS.

@@

Of particular interest is that last feature, \lstinline{watch}. We use grunt's \lstinline{watch} capability to run tests constantly. This feature gives immediate feedback to the developer when they change existing code or write new code after having written a test for it. As long as all the tests are passing, the developer has a good idea that the changes made are regression-tested as well as freshly tested and are ready for publishing or integration.

@@

\normalsize
%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Framework Selection}
In this chapter, we will outline our final choices for frameworks and why we chose them.

\section{Chosen Tools}
After evaluating a number of different combinations and tools, we came to the following setup:
\begin{itemize}
  \item Unit Testing: Mocha with Chai.js
  \item Continuous Integration: MagnumCI
  \item Browser Testing: Nightwatch
  \item Misc:
    \begin{itemize}
      \item Coverage: Istanbul
      \item Task Runner: Grunt
      \item Package Manager: NPM (sort of a given when working with Node.js)
    \end{itemize}
\end{itemize}

@@

Mocha was chosen over QUnit because of the ability to structurally portray test suites. Although QUnit output a more thorough test summary, the ability to scan code more efficiently was of greater importance to us.

@@

\subsection{MagnumCI}
MagnumCI has all of the features that a developer might need for free. We are still confident that the features needed by an open-source developer will continue to be free after MagnumCI ends its open-beta period.

Given enough resources and time, Jenkins will offer more support and functionality than the rest of the CI frameworks. However, there's something to be said for ease of setup and total time to first use of a tool. MagnumCI offered quick initialization through web pages and automatic repository connections that allow users to quickly configure and run the CI framework.

MagnumCI was chosen over Travis because our evaluation application was not on GitHub. Travis is still an incredible CI framework that has some of the best documentation among the CI frameworks. If a developer has their project on GitHub, we would recommend Travis over MagnumCI.

Semaphore's lack of support for JavaScript and Node.js projects as well as the GitHub requirement kept us from choosing it.

@@

Overall, the CI frameworks were all impressive and usable. The main driving factor behind our decision was that our application used a custom repository and that at the time of this writing our application is closed-source. We have every intention of opening it to the public as soon as we get a version that is more polished.

@@

Nightwatch was chosen over Intern's UI testing tool because of the issue with Intern running its own server. If Intern did not impose its own server for what it calls ``functional'' testing, we would probably have gone with Intern for both Unit and UI testing. Intern is a strong choice for an all-in-one testing tool.

@@

Istanbul was chosen because of the ease of set up in getting it running using our existing toolset and project. There are other code coverage tools but Istanbul required so little setup that we chose to not look further.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Product 
%%% User Manual
%%%   Tools (programs, IDEs, scripts)
%%%   Setup instructions
%%%   Usage
%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Testing and Development Workflow}
In this section we will mention our development setup, discuss how to set up the chosen tools, and outline our recommended workflow using the tools. It is our hope that after finishing this section, the reader will be able to install and run the chosen tools and have a good grasp of what the next steps are for their particular project.

\section{Our Implementation Configuration}
The following are the specs of the laptop that we used for the entirely of this research and implementation:
\begin{itemize}
  \item Model: 15-inch Macbook Pro, Late 2008
  \item OS: OS X 10.9.2, Mavericks
  % \item Processor: 2.53 GHz Intel Core 2 Duo
  % \item Memory: 4 GB 1067 MHz DDR3
  % \item Graphics: NVIDIA GeForce 9400M 256 MB
\end{itemize}
The point of listing the laptop specs is to show that our research and workflow was completed on an average, everyday laptop and does not require any kind of special hardware or software configurations. In addition, our setup instructions will be OS X based, but nearly all commands will work the same on another UNIX-based system.

@@

\section{Tool Setup}
Getting the tools up and running is a fairly simple task. It involves installing modules with NPM, writing or copying a few configuration scripts, and then using the terminal commands for running the tests.

We decided to install the node modules globally, but it's not a requirement. Tests can be executed using locally installed node modules. Instead of using the command by itself, the developer would just need to supply the full path to the executable, which is generally \lstinline{./node_modules/MODULE_NAME/bin/MODULE_NAME} \space instead of \lstinline{MODULE_NAME}. For example, a globally installed Mocha executable can be run with \lstinline{mocha ...} while a locally installed Mocha module is run with \lstinline{./node_modules/mocha/bin/mocha ...} \space .
